Outstanding Title

### 2017-05-02 writing/EpiDraft.Rmd
Turn code chunk evaluation back on for the moment
sd=1 default in create_sims

```{r echo = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

@@

>>>>

```{r echo = FALSE}
# knitr::opts_chunk$set(eval = FALSE)
```

@@

save(leg_cases, file="data/leg_cases.rda")

```{r}
#Checking for anomalies:
leg_cases[which(leg_cases$checkma != "MID. ATLANTIC"),]
leg_cases[which(leg_cases$checknyc != "N.Y. City"),]
leg_cases[which(leg_cases$checkpa != "Pa."),]

#Row 48 is the only row with different states. 569 and 574 have NA in every column.
```

```{r}
#Power analysis using eesim
